---
title: "Imagery and phenomenological control"
output: html_document
date: "2023-02-28"
---

#load libraries
```{r setdup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(ggstatsplot)
library(readxl)
library(scales)
library(ggside)
library(cocor)
library(bfrr) #install by running: (devtools::install_github("debruine/bfrr")
library(effectsize)
sessionInfo() #Print version information about R, the OS and attached or loaded packages 
myseed <- 1 #set seed for reproducible figures
```

# Experiment 1 
### import pcs and swash datasets, filter by Experiment 1 and check age/gender
```{r setdup88, include=FALSE}
data_swash<-read_xlsx("swash_vviq_full.xlsx") #import swash
data_pc<-read_xlsx("pcs_vviq_full.xlsx") #import pc 
data_pc$Age<-as.integer(as.character(data_pc$Age))
data_pc$Experiment<-as.factor(data_pc$Experiment)
#Generate column with VVIQ ranging from 0 to 4
data_pc$VVIQ_rescaled <- scales::rescale(data_pc$VVIQ, to = c(0, 4))
data_swash$VVIQ_rescaled <- scales::rescale(data_swash$VVIQ, to = c(0, 4))

data_swash_1 <- filter (data_swash, 
                   Experiment == "Experiment 1") #keep only Exp 1 participants
data_pc_1 <- filter (data_pc, 
                   Experiment == "Experiment 1") #keep only Exp 1 participants

#Age & Gender SWASH as shown in participants section
meanage_swash_exp1<-round(mean(data_swash_1$Age), digits=2) #round for reporting
sdage_swash_exp1<-round(sd(data_swash_1$Age), digits=2)#round for reporting
range_age_swash_exp1 <- c(min(data_swash_1$Age), max(data_swash_1$Age))
gender_swash_exp1<-table(data_swash_1$Gender)#round for reporting

#Age & Gender PC
meanage_pcs_exp1<-round(mean(data_pc_1$Age), digits=2)#round for reporting
sdage_pcs_exp1<-round(sd(data_pc_1$Age), digits=2)#round for reporting
range_age_pcs_exp1<-c(min(data_pc_1$Age), max(data_pc_1$Age)) 
gender_pcs_exp1<-table(data_pc_1$Gender)

```

## Experiment 1: Relationship between SWASH and VVIQ
```{r setdup22}
#descriptives: mean and SD for SWASH scale
mean_swash=mean(data_swash_1$SWASH)
sd_swash=sd(data_swash_1$SWASH)
round(mean_swash, digits=2) #display rounded to 2 decimals
round(sd_swash, digits=2)#display rounded to 2 decimals

#descriptives: mean and SD for VVIQ scale
mean_vviq_swash=mean(data_swash_1$VVIQ_rescaled)
sd_vviq_swash=sd(data_swash_1$VVIQ_rescaled)
round(mean_vviq_swash, digits=2) #display rounded to 2 decimals
round(sd_vviq_swash, digits=2)#display rounded to 2 decimals

#linear model predicting SWASH score based on VVIQ score
swash1 <- lm(SWASH ~ VVIQ_rescaled, data = data_swash_1)
output_swash1 <- summary(swash1) 
print(output_swash1) #for bf, we need estimate, SE
round(output_swash1$coefficients["VVIQ_rescaled", "Estimate"], digits=2) #display beta rounded to 2 decimals 
round(output_swash1$coefficients["VVIQ_rescaled", "t value"], digits=2) #round t value
round(output_swash1$coefficients["VVIQ_rescaled", "Pr(>|t|)"], digits=2) #round p value
round(output_swash1$coefficients["VVIQ_rescaled", "Std. Error"], digits=2) #round se
round(output_swash1$adj.r.squared, digits=2) #round r squared
CI_b_swash1 <- round(confint(swash1, 'VVIQ_rescaled', level=0.95), digits=2) #confidence interval for b 
CI_b_swash1

#extract values for BF calculation
mean_effect <-output_swash1$coefficients["VVIQ_rescaled", "Estimate"]
se_effect <-  output_swash1$coefficients["VVIQ_rescaled", "Std. Error"]
sd_theory=(mean_swash/mean_vviq_swash)/2
round(sd_theory, digits=2) #display rounded to 2 decimals
sample_swashdf=nrow(data_swash_1)-2 #calculate degrees of freedom

#Bayes factor + Robustness region for "Relationship between SWASH and VVIQ"
rr_swash1 <- bfrr(
    sample_mean = mean_effect, # mean of the sample
    sample_se = se_effect, # SE of the sample
    sample_df=sample_swashdf,
    model = "normal",
    mean = 0, # mean of the H1 distribution
    sd = sd_theory, # SD of the H1 distribution
    tail = 1, # is the test 1-tailed or 2-tailed
    criterion = 3, # BF against which to test for support for H1/H0
    precision = 0.001 # precision to vary RR parameters
)
summary(rr_swash1)
round(rr_swash1$RR$sd, digits=2) #round rr

#swash x vviq plot, Figure 1
plot_swash1<-ggscatterstats(
    data = data_swash_1,
    x =VVIQ_rescaled, bf.message = FALSE, results.subtitle = FALSE,
    y = SWASH,
    xlab = "VVIQ",
    ylab = "SWASH", xsidehistogram.args = list(fill = "#329896", color = "black", na.rm = TRUE), ysidehistogram.args = list(fill = "#B657CA", color = "black", na.rm = TRUE), title = "", ggtheme = ggplot2::theme_light(base_size = 15), plot.title = element_text(size=22), ggplot.component = list(ggplot2::scale_y_continuous(breaks = seq(0, 5, 1), limits=c(0, 5)), scale_x_continuous(breaks = seq(0, 4, 1), limits=c(0, 4))
    ))+ ggpubr::theme_pubr()
ggsave(plot =plot_swash1, paste("figure1_", Sys.Date(), ".tiff", sep = ""), width = 200, height =170, units="mm") #this helps generating a figure without overwriting the one already present
round(cor(data_swash_1$VVIQ_rescaled, data_swash_1$SWASH, method="spearman"), digits=2) #spearman r to report under plot
```

## Experiment 1: Relationship between PCS and VVIQ
```{r setdup22_pc}
#descriptives
mean_pcs=mean(data_pc_1$Pcscore) #calculate mean pcs
round(mean_pcs, digits=2) #display rounded to 2 decimals
sd_pcs=sd(data_pc_1$Pcscore)
round(sd_pcs, digits=2) #display rounded to 2 decimals
mean_vviq_pcs=mean(data_pc_1$VVIQ_rescaled) #calculate mean vviq
round(mean_vviq_pcs, digits=2) #display rounded to 2 decimals
sd_vviq_pcs=sd(data_pc_1$VVIQ_rescaled) #calculate sd vviq
round(sd_vviq_pcs, digits=2)#display rounded to 2 decimals

pc1 <- lm(Pcscore ~ VVIQ_rescaled, data = data_pc_1) #model pcscore predicted by vviq 
output_pc1 <- summary(pc1)
print(output_pc1) #for bf, we need estimate, SE
round(output_pc1$coefficients["VVIQ_rescaled", "Estimate"], digits=2) #round beta
round(output_pc1$coefficients["VVIQ_rescaled", "Std. Error"], digits=2) #round SE
round(output_pc1$coefficients["VVIQ_rescaled", "t value"], digits=2) #round t value
round(output_pc1$coefficients["VVIQ_rescaled", "Pr(>|t|)"], digits=3) #round p value
round(output_pc1$adj.r.squared, digits=2) #round r squared
CI_b_pc1 <- round(confint(pc1, 'VVIQ_rescaled', level=0.95), digits=2) #confidence interval for b 
CI_b_pc1
mean_effect_pc1 <- output_pc1$coefficients["VVIQ_rescaled", "Estimate"] #extract mean effect for BF calculation as the beta
se_effect_pc <- output_pc1$coefficients["VVIQ_rescaled", "Std. Error"] #extract se of model
sd_theory_pc<-(mean_pcs/mean_vviq_pcs)/2 #sd theory
round(sd_theory_pc, digits=2) #round just for reporting
sample_pcdf<-nrow(data_pc_1)-2 # calculate degrees of freedom

#Bayes factor + Robustness region for "Relationship between PCS and VVIQ"
rr_pc1 <- bfrr(
    sample_mean = mean_effect_pc1, # mean of the sample
    sample_se = se_effect_pc, # SE of the sample
    sample_df = sample_pcdf,
    model = "normal",#or normal 
    mean = 0, # mean of the H1 distribution
    sd = sd_theory_pc, # SD of the H1 distribution
    tail = 1, # is the test 1-tailed or 2-tailed
    criterion = 3, # BF against which to test for support for H1/H0
    precision = 0.001 # precision to vary RR parameters
)
summary(rr_pc1)
round(rr_pc1$RR$sd, digits=2) #round rr


#let's plot pc x vviq, Figure 2
plot_pc1<-ggscatterstats(
    data = data_pc_1,
    x =VVIQ_rescaled, bf.message = FALSE, results.subtitle = FALSE,
    y = Pcscore,
    xlab = "VVIQ",
    ylab = "PCS", xsidehistogram.args = list(fill = "#329896", color = "black", na.rm = TRUE), ysidehistogram.args = list(fill = "#B657CA", color = "black", na.rm = TRUE),
    title = "", ggtheme = ggplot2::theme_light(base_size = 15), plot.title = element_text(size=22), ggplot.component = list(ggplot2::scale_y_continuous(breaks = seq(0, 5, 1), limits=c(0, 5)), scale_x_continuous(breaks = seq(0, 4, 1), limits=c(0, 4))
    ))+ ggpubr::theme_pubr()
ggsave(plot =plot_pc1, paste("figure2_", Sys.Date(), ".tiff", sep = ""), width = 200, height =170, units="mm") #this helps generating a figure without overwriting the one already present
round(cor(data_pc_1$VVIQ_rescaled, data_pc_1$Pcscore, method="spearman"), digits=2) #calculate and round spearman's r reported under figure

```

## Experiment 1: Slope comparison between VVIQxSWASH and VVIQxPCS
```{r setdup99}
sample1<-subset(data_swash_1, select=c(VVIQ_rescaled, SWASH)) #storing data as cocor wants
sample2<-subset(data_pc_1, select=c(VVIQ_rescaled, Pcscore)) #storing data as cocor wants

dat_list <- list(sample2 = as.data.frame(sample2),
                 sample1 = as.data.frame(sample1))
slopecomp<-cocor(formula = ~VVIQ_rescaled + Pcscore | VVIQ_rescaled + SWASH, 
      data = dat_list) #formula for comparing slopes

round(slopecomp@fisher1925$statistic, digits=2) #round z stat
round(slopecomp@fisher1925$p.value, digits=2) #round p value
round(slopecomp@zou2007$conf.int, digits=2) #round 95% CI 

sample_mean_comp<- slopecomp@diff
sample_se_comp=slopecomp@diff/slopecomp@fisher1925$statistic
sd_theory=0.12 #explained in paper, prior based on Glisky et al., 1995

#BF for slope comparison between SWASH x VVIQ and PCS x VVIQ
rr_slopecomp <- bfrr(
    sample_mean = sample_mean_comp, # mean of the sample
    sample_se =sample_se_comp, # SE of the sample
    model = "norm",#or normal 
    mean = 0, # mean of the H1 distribution
    sd = sd_theory, # SD of the H1 distribution
    tail = 1, # is the test 1-tailed or 2-tailed
    criterion = 3, # BF against which to test for support for H1/H0
    precision = 0.001 # precision to vary RR parameters
)
summary(rr_slopecomp)
round(rr_slopecomp$RR$sd, digits=2) #round rr

```

## Experiment 1: Comparing PCS of aphantasics with non aphantasics
```{r setdusksp}
data_pc_1$Group<-as.factor(as.character(data_pc_1$Group))
summary_pcs_aphnoap <- data_pc_1 %>% 
    group_by(Group) %>%
    summarise(mean_pc=mean(Pcscore), sd_pc=sd(Pcscore), mean_vviq=mean(VVIQ_rescaled), sd_vviq=sd(VVIQ_rescaled)) #calculate stats summary pcs vviq for both groups

data_pc_1 %>% #print same stats with rounded values for reporting
    group_by(Group) %>%
    summarise(mean_pc=round(mean(Pcscore), digits=2), sd_pc=round(sd(Pcscore), digits=2), mean_vviq=round(mean(VVIQ_rescaled), digits=2), sd_vviq=round(sd(VVIQ_rescaled), digits=2))

pc2 <- t.test(data_pc_1$Pcscore ~ data_pc_1$Group) #t test with unaware aphants vs non aphants
pc2
round(pc2$parameter, digits=2) #round df
round(pc2$statistic, digits=2) #round t value
round(pc2$p.value, digits=2) #round p value to 2 digits (it's 0.018 so it has to be rounded to 2 digits)
round(pc2$conf.int, digits=2) #round confidence
hedges_g(data_pc_1$Pcscore ~ data_pc_1$Group) #95% CI for Hedges’ g is not reported in the manuscript to avoid confusion with the 95% CI reported in the same sentence

mean_diff <- summary_pcs_aphnoap$mean_pc[2] - summary_pcs_aphnoap$mean_pc[1] #substract mean pc non-aphants minus mean pc aphants #substract mean pc non-aphants minus mean pc aphants
se_diff<-mean_diff/as.double(pc2$statistic) # divide mean diff by pc2 t-statistics
abs(round(se_diff, digits=2)) #round SE for reporting
sd_theory_diff<- (summary_pcs_aphnoap$mean_pc[2])/2 #half the mean non-aphants
round(sd_theory_diff, digits=2) #for reporting 
df_pcaph<-as.double(pc2$parameter)
#rr for "PCS between aphants and non-aphants"
rr_pc2 <- bfrr(
    sample_mean = mean_diff, # mean of the sample
    sample_se =se_diff,# SE of the sample
    sample_df=df_pcaph, #pc2 t-test sample df
    model = "normal", #or normal 
    mean = 0, # mean of the H1 distribution
    sd = sd_theory_diff, # half 
    tail = 1, # is the test 1-tailed or 2-tailed
    criterion = 3, # BF against which to test for support for H1/H0
    precision = 0.001 # precision to vary RR parameters
)
summary(rr_pc2)
round(rr_pc2$RR$sd, digits=2) #round rr
```


# Experiment 2
## checking age & descriptives
```{r setdup55}
#to check *included* aphants age swash
summary_age2 <- data_swash %>%
    group_by(Group) %>%
    summarise(mean_age=round(mean(Age), digits=2), sd_age=round(sd(Age), digits=2), min=round(min(Age), digits=2), max=round(max(Age), digits=2))

summary_gender2<- data_swash %>% #gender info for self-repo aph
    group_by(Group, Gender) %>%
    summarise(n=n())

#to check *included* aphants age pc
summary_age <- data_pc %>%
    group_by(Group) %>%
    summarise(mean_age=round(mean(Age), digits=2), sd_age=round(sd(Age), digits=2), min=round(min(Age), digits=2), max=round(max(Age), digits=2))

summary_gender22<- data_pc %>% #gender info for self-reported aph
    group_by(Group, Gender) %>%
    summarise(n=n())

#participants section: compare age differences between study 1 and 2
#age comparison with study 1 
agetest_swash<-t.test(data_swash$Age~data_swash$Experiment) #t test to compare age diff between study 1 SWASH sample and study 2 SWASH sample
round(agetest_swash$parameter, digits=2) #round df
round(agetest_swash$statistic, digits=2) #round t value
round(agetest_swash$p.value, digits=2) #round p value to 2 digits (it's 0.018 so it has to be rounded to 2 

agetest_pc<-t.test(data_pc$Age~data_pc$Experiment) #t test to compare age diff between study 1 PCS sample and study 2 PCS sample
round(agetest_pc$parameter, digits=2) #round df
round(agetest_pc$statistic, digits=2) #round t value
round(agetest_pc$p.value, digits=2) #round p value to 2 digits (it's 0.018 so it has to be rounded to 2 
```


## Experiment 2: SWASH comparison Exp2 aphantasics
```{r set550}
# comparison SWASH between non-aphantasics and self-reported aphantasics
#summary descriptives swash+vviq per group
summary_swash22 <- data_swash %>%
    group_by(Group) %>%
    summarise(mean=mean(SWASH), sd=sd(SWASH), mean_vviq=mean(VVIQ_rescaled), sd_vviq=sd(VVIQ_rescaled), n=n())

# rounding ONLY for reporting
data_swash %>%
    group_by(Group) %>%
    summarise(mean=round(mean(SWASH), digits=2), sd=round(sd(SWASH), digits=2), mean_vviq=round(mean(VVIQ_rescaled), digits=2), sd_vviq=round(sd(VVIQ_rescaled), digits=2))


data_swash_2 <- filter (data_swash, 
                   !Group == "Blinded aphantasics") #remove blinded aphants 

data_swash_2$Group<-as.factor(as.character(data_swash_2$Group))
swash2<- t.test(data_swash_2$SWASH ~ data_swash_2$Group)
round(swash2$parameter, digits=2) #round df
round(swash2$statistic, digits=2) #round t value
round(swash2$conf.int, digits=2) #round confidence

hedges_g(data_swash_2$SWASH ~ data_swash_2$Group)


sample_mean_swashdiff<-summary_swash22$mean[2] - summary_swash22$mean[3]
 #mean non aphantasics - mean self-reported aphants
sample_se_swashdiff<-sample_mean_swashdiff/as.double(swash2$statistic)
round(sample_se_swashdiff, digits=2)
upper_swashdiff=summary_swash22$mean[2]
rr_swash2 <- bfrr(
    sample_mean = sample_mean_swashdiff, # mean of the sample
    sample_se = sample_se_swashdiff, # SE of the sample
    model = "uniform", #or normal 
    lower = 0, # mean of the H1 distribution
    upper = upper_swashdiff, # SD of the H1 distribution
    criterion = 3, rr_interval = list( # ranges to vary H1 parameters for robustness regions
       lower = c(0, 0), # explore H1 means from 0 to 2
       upper = c(0, upper_swashdiff) # explore H1 SDs from 0 to 2
    ), precision = 0.001, 
)
summary(rr_swash2)
sprintf("%.2e", rr_swash2$BF) #BF to scientific for reporting
round(rr_swash2$RR$upper, digits=2) #round rr

set.seed(myseed) #this needs to be repeated before each figure with jittered dots
#plot mean swash for non aph and aph (Figure 3)
plot_swash2<-ggbetweenstats(
    data = data_swash_2,
    x = Group,
    results.subtitle = FALSE, 
    y = SWASH,
    grouping.var = group,type = "p", 
    p.adjust.method="none",
    title =, 
    point.path.args = list(alpha = 0.3, linetype = "dotted"), 
    bf.message=TRUE, 
    xlab = "",
    ylab = "SWASH", ggplot.component = list(ggplot2::scale_y_continuous(breaks = seq(0, 5, 1), limits=c(0, 5))))+
    ggpubr::theme_pubr(legend="none")
ggsave(plot =plot_swash2, paste("figure3_", Sys.Date(), ".tiff", sep = ""), width = 190, height =130, units="mm") #this helps generating a figure without overwriting the one already present
```

# self-reported aphantasics vs  swash ~ vviq linear model intercept (from Experiment 1)
```{r set55990}
output_swash1 #run this to see the model where we take the intercept from
swash_intercept=output_swash1$coefficients["(Intercept)", "Estimate"] #extract model intercept
round(swash_intercept, digits=2)  #round intercept for reporting
se_intercept1=output_swash1$coefficients["(Intercept)", "Std. Error"] #extract intercept se
round(se_intercept1, digits=2) #round intercept se for reporting
mean_swash_selfaph<-summary_swash22$mean[3] #extract self-reported aphantasics mean swash
#t test with intercept of linear model vviq x SWASH and self-reported aphants.
SE_aphants=summary_swash22$sd[3]/sqrt(summary_swash22$n[3]) #divide sd self-reporte df aphantasics by number of self-reported aphantasics
dfi<- nrow(data_swash_1)-2 # df of VVIQ x SWASH linear model
dfaph<- summary_swash22$n[3] #number of self-reported aphantasics
#df = dfintercept + dfaph
dftot<-dfi+dfaph
#Mean difference  = Intercept-mean self-reportedaphantasics 
Meandifference= swash_intercept-mean_swash_selfaph
#SEdiff = sqrt((SE_Intercept)^2+(SE_aphantasics)^2)
SEdiff = sqrt((se_intercept1)^2+(SE_aphants)^2)
round(SEdiff, digits=2) #round for reporting
#t = (mean difference) / SEdiff
t = Meandifference / SEdiff
round(t, digits=2)
#Calculate 95% Ci for the t test
SD_intercept=se_intercept1*sqrt(dfi)
sd2=summary_swash22$sd[3] #sd of aphantasics
sd1=SD_intercept
num1<-dfi #df swash intercept
num2<-dfaph #aphants
m1=swash_intercept #intercept estimate
m2=mean_swash_selfaph #mean self-reported aphantasics
se <- sqrt(sd1*sd1/num1+sd2*sd2/num2)#calculate se of sample for BF
round(se, digits=2)
error <- qt(0.975,df=pmin(num1,num2)-1)*se #calculate error for 95% CI 
left <- (m1-m2)-error #lower 95% CI
round(left, digits=2)  #round lower 95% CI
right <- (m1-m2)+error #upper 95% CI
round(right, digits=2) #round upper 95% CI
pvalue1=pt(q=t, df=dftot, lower.tail=FALSE)
round(pvalue1, digits=3)
#bf for intercept test
rr_inter <- bfrr(
    sample_mean = Meandifference, # mean difference
    sample_se = se, # SE of the sample
    model = "uniform", #or normal 
    lower = 0, # mean of the H1 distribution
    upper = m1, # SD of the H1 distribution
    criterion = 3, rr_interval = list( # ranges to vary H1 parameters for robustness regions
       lower = c(0, 0), # explore H1 means from 0 to 2
       upper = c(0, m1) # explore H1 SDs from 0 to 2
    ), precision = 0.001, 
)
summary(rr_inter)
round(rr_inter$RR$upper, digits=2) #round rr

```


## Experiment 2: comparisons PCS Exp2 in the non-aphantasics vs self-reported aphantasics
```{r set556}
#summary descriptives pcs+vviq per group
summary_pcs22 <- data_pc %>%
    group_by(Group) %>%
    summarise(mean=mean(Pcscore), sd=sd(Pcscore), mean_vviq=mean(VVIQ_rescaled), sd_vviq=sd(VVIQ_rescaled), n=n())

# rounding ONLY for reporting!!
data_pc %>%
    group_by(Group) %>%
    summarise(mean=round(mean(Pcscore), digits=2), sd=round(sd(Pcscore), digits=2), mean_vviq=round(mean(VVIQ_rescaled), digits=2), sd_vviq=round(sd(VVIQ_rescaled), digits=2))

#comparison PCS between Exp1 non-aphantasics and Exp2 self-reported aphantasics
data_pc_2 <- filter (data_pc, 
                   !Group == "Blinded aphantasics") #remove blinded aphantasics for the comparison non-aphantasics Study 1 vs self-reported aphantasics Study 2

summary_pcs22 #this is the tibble where we get the data from

mean_pc_selfaph<-summary_pcs22$mean[3] 
mean_pc_noaph<-summary_pcs22$mean[2]


data_pc_2$Group<-as.factor(as.character(data_pc_2$Group))
pcs33<- t.test(data_pc_2$Pcscore~ data_pc_2$Group)
round(pcs33$parameter, digits=2) #round df
round(pcs33$statistic, digits=2) #round t value
abs(round((mean_pc_noaph-mean_pc_selfaph)/as.double(pcs33$statistic),digits=2)) #round se
round(pcs33$conf.int, digits=2) #round confidence
round(pcs33$p.value, digits=3) #round confidence
hedges_g(data_pc_2$Pcscore~ data_pc_2$Group)

mean_difference_pcs<-mean_pc_noaph-mean_pc_selfaph #difference between mean non-aphantsics - mean self-reported aphantasics
se_difference_pcs<-mean_difference_pcs/as.double(pcs33$statistic) #divide mean difference by t-statistics
#bf for comparison PCS  between unaware aphantasics and self-reported aphantasics
rr_aphnoap_pc <- bfrr(
    sample_mean = mean_difference_pcs, # mean of the sample
    sample_se = se_difference_pcs, # SE of the sample
    model = "uniform", #or normal 
    lower = 0, # mean of the H1 distribution
    upper = mean_pc_noaph, # menan non-aphants
    criterion = 3, rr_interval = list( # ranges to vary H1 parameters for robustness regions
       lower = c(0, 0), # explore H1 means from 0 to 2
       upper = c(0, mean_pc_noaph) # explore H1 SDs from 0 to 2
    ), precision = 0.001, 
)
summary(rr_aphnoap_pc)
sprintf("%.2e", rr_aphnoap_pc$BF) #BF to scientific for reporting
round(rr_aphnoap_pc$RR$upper, digits=2) #round rr
```

## Exp2: comparison between intercept of Experiment 1 linear model  PCS ~ VVIQ (PCS when VVIQ=0) and self-reported aphantasics
```{r set55f6}
output_pc1 #this is Experiment 1 model where we take the intercept from
pc_intercept=output_pc1$coefficients["(Intercept)", "Estimate"]
round(pc_intercept, digits=2)
se_intercept=output_pc1$coefficients["(Intercept)", "Std. Error"]
round(se_intercept, digits=2)
#t test with intercept of linear model  PCS ~ VVIQ (VVIQ=0) and self-reported aphants
dfi_pc<-  nrow(data_pc_1)-2 #df VVIQ ~ PCS linear model
dfaph_pc<- summary_pcs22$n[3] #n self-reported pahants
SE_aphants=summary_pcs22$sd[3]/sqrt(summary_pcs22$n[3]) #se self-reported aphantasics
#df = dfintercept + dfaph
dftot_pc<-dfi_pc+dfaph_pc
Mean_difference_pc  = pc_intercept-mean_pc_selfaph  #difference between  PCS  ~ VVIQ model intercept and mean PCS self-reported aphants
SEdiff_pc = sqrt((se_intercept)^2+(SE_aphants)^2) #SEdiff = sqrt((SE_Intercept)^2+(SE_aphantasics)^2)
round(SEdiff_pc, digits=2) #round SE for reporting
t_pc = Mean_difference_pc / SEdiff_pc #t = (mean difference) / SEdiff
round(t_pc, digits=2) #round t value for reporting
#Calculate 95% Ci for the t test
SD_intercept_pc=se_intercept*sqrt(dfi_pc)
sd2_pc=summary_pcs22$sd[3] #sd of aphantasics
sd1_pc=SD_intercept_pc
num1_pc<-dfi_pc
num2_pc<-dfaph_pc
m1_pc=pc_intercept
m2_pc=mean_pc_selfaph 
se_pc <- sqrt(sd1_pc*sd1_pc/num1_pc+sd2_pc*sd2_pc/num2_pc)
error_pc <- qt(0.975,df=pmin(num1_pc,num2_pc)-1)*se_pc
left_pc <- (m1_pc-m2_pc)-error_pc #calculate 95% CI (left)
round(left_pc, digits=2) #round left 95% CI
right_pc <- (m1_pc-m2_pc)+error_pc #calculate 95% CI (right)
round(right_pc, digits=2) #low right 95% CI for reporting
pvalue=pt(q=t_pc, df=dftot_pc, lower.tail=FALSE) #no need to round pvalue as it's clear less than 001

#bf for comparison intercept unaware and self-reported aphants, PCS
rr_inter2 <- bfrr(
    sample_mean = Mean_difference_pc, # mean of the sample
    sample_se = SEdiff_pc, # SE of the sample
    model = "uniform", #or normal 
    lower = 0, # mean of the H1 distribution
    upper = m1_pc, # SD of the H1 distribution
    criterion = 3, rr_interval = list( # ranges to vary H1 parameters for robustness regions
       lower = c(0, 0), 
       upper = c(0, m1_pc) 
    ), precision = 0.001, 
)
summary(rr_inter2)
sprintf("%.2e", rr_inter2$BF) #BF to scientific for reporting
round(rr_inter2$RR$upper, digits=2) #round rr

```


## Comparison of PCS with unaware aphantasics based on cut-off of rescaled VVIQ <=1
```{r set5586}
data_pc_3 <- filter (data_pc, 
                   !Group == "Non-aphantasics") #remove non-aphantasics group to compare unaware and self-reported aphantasics
mean_pc_unaware<-summary_pcs22$mean[1] #extract blinded aphantasics mean
data_pc_3$Group<-as.factor(as.character(data_pc_3$Group)) 
t_extreeme<- t.test(data_pc_3$Pcscore~ data_pc_3$Group) #t-test to compare unaware and self-reported
round(t_extreeme$parameter, digits=2) #round df
round(t_extreeme$statistic, digits=2) #round t value
round((mean_pc_unaware-mean_pc_selfaph)/as.double(t_extreeme$statistic), digits=2) #calculate and round se
round(t_extreeme$conf.int, digits=2) #round confidence
hedges_g(data_pc_3$Pcscore ~ data_pc_3$Group) #effect size


#summary_pcs22 #run this to check the tibble where we take the means from
mean_diff_aph<-mean_pc_unaware-mean_pc_selfaph #calculate diff mean blinded - self-reported aphantasics
se_diff_aph<-mean_diff_aph/as.double(t_extreeme$statistic) #divide mean by t.statistic
#bf for comparison PCS  between blinded aphantasics and self-reported aphantasics
abs(round(se_diff_aph, digits=2))
rr_aphnoap2 <- bfrr(
    sample_mean = mean_diff_aph, # mean of the sample
    sample_se = se_diff_aph, # SE of the sample
    model = "uniform", #or normal 
    lower = 0, # mean of the H1 distribution
    upper = mean_pc_unaware, # SD of the H1 distribution
    criterion = 3, rr_interval = list( # ranges to vary H1 parameters for robustness regions
       lower = c(0, 0), # explore H1 means from 0 to 2
       upper = c(0, mean_pc_unaware) # explore H1 SDs from 0 to 2
    ), precision = 0.001, 
)
summary(rr_aphnoap2)
sprintf("%.2e", rr_aphnoap2$BF) #BF to scientific for reporting
round(rr_aphnoap2$RR$upper, digits=2) #round rr

# Generate Figure 4
#let's re-order the group variable prior to plotting -> please note this is done just for generating the figure
data_pc2<- data_pc #save data_pc into new dataframe to avoid confusion with order
data_pc2$Group <- factor(data_pc2$Group, levels = c("Non-aphantasics", "Blinded aphantasics", "Self-reported aphantasics"))

#plot mean pc for non aphantasics, unaware and self-reported aphantasics (Figure 4)
set.seed(myseed) #this needs to be repeated before each figure with jittered dots
plot_aphnoaph_pc<- ggbetweenstats(
    data = data_pc2,
    x = Group,
    results.subtitle = FALSE, 
    pairwise.comparisons = FALSE,
    y = Pcscore,
    grouping.var = group,
    title ="", 
    point.path.args = list(alpha = 0.3, linetype = "dotted"), 
    bf.message=FALSE, 
    xlab = "",
    ylab = "PCS", ggplot.component = list(ggplot2::scale_y_continuous(breaks = seq(0, 5, 1), limits=c(0, 5))))+
    ggpubr::theme_pubr(legend="none")
ggsave(plot =plot_aphnoaph_pc, paste("figure4_", Sys.Date(), ".tiff", sep = ""), width = 270, height =150, units="mm") #this helps generating a figure without overwriting the one already present
```


